---
title: "Linear models"
output: github_document
---

load packages
```{r}
library(tidyverse)
library(p8105.datasets)

```


setup
```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "right"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Load and clean Airbnb data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  select(price, stars, borough = neighbourhood_group, neighbourhood, room_type) |> 
  filter(borough != "Staten Island")

```

Let's fit a model!

```{r}
fit = 
  nyc_airbnb |> 
  lm(price ~ stars + borough, data = _)
```

Let's look at 'fit'
can do these but none are particularly helpful
```{r}
fit
summary(fit)
summary(fit)$coef
coef(fit)
#fitted.values(fit)

```

Instead let's tidy up the output
glance good way to get at AIC and BIC

```{r}
fit |> 
  broom::glance()
```


or use tidy to tidy up the coefficients
```{r}
fit |> 
  broom::tidy() |> 
  mutate(term = str_replace(term, "^borough", "Borough:")) |> 
  select(term, estimate, p.value) |> 
  knitr::kable(digits = 3)
```

broom is great bc they generate tibbles

#Fit another model
define factor ordering to define your reference; otherwise just does alphabetical order
our reference category is manhattan; so each borough is being compared to manhattan
like queens is less than manhattan keeping stars and room type fixed
```{r}
fit = 
  nyc_airbnb |> 
  mutate(borough = fct_infreq(borough),
         room_type = fct_infreq(room_type)) |> 
  lm(price ~ stars + borough + room_type, data = _)

fit |> 
  broom::tidy()
```



