---
title: "Linear models"
output: github_document
---

load packages
```{r}
library(tidyverse)
library(p8105.datasets)

```


setup
```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "right"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Load and clean Airbnb data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  select(price, stars, borough = neighbourhood_group, neighbourhood, room_type) |> 
  filter(borough != "Staten Island")

```

Let's fit a model!

```{r}
fit = 
  nyc_airbnb |> 
  lm(price ~ stars + borough, data = _)
```

Let's look at 'fit'
can do these but none are particularly helpful
```{r}
fit
summary(fit)
summary(fit)$coef
coef(fit)
#fitted.values(fit)

```

Instead let's tidy up the output
glance good way to get at AIC and BIC

```{r}
fit |> 
  broom::glance()
```


or use tidy to tidy up the coefficients
```{r}
fit |> 
  broom::tidy() |> 
  mutate(term = str_replace(term, "^borough", "Borough:")) |> 
  select(term, estimate, p.value) |> 
  knitr::kable(digits = 3)
```

broom is great bc they generate tibbles

#Fit another model
define factor ordering to define your reference; otherwise just does alphabetical order
our reference category is manhattan; so each borough is being compared to manhattan
like queens is less than manhattan keeping stars and room type fixed
```{r}
fit = 
  nyc_airbnb |> 
  mutate(borough = fct_infreq(borough),
         room_type = fct_infreq(room_type)) |> 
  lm(price ~ stars + borough + room_type, data = _)

fit |> 
  broom::tidy()
```

# Quick look at diagnostics
get residuals and inspect them; too make sure you dont' have super skewed distrubtion etc

our model that we created is fit
```{r}
nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = resid)) +
  geom_density()
```

look at residuals and predictors (your x's)
```{r}
nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = borough, y = resid)) +
  geom_violin()

nyc_airbnb |> 
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = stars, y = resid)) +
  geom_point()
```
seeing some skew
might want to do a bootstrap or diff model other than lm

## Hypothesis test for categorical predictor

fit a "null" and "alternative" model
let's see if room type is signif
use anova to compare

```{r}
fit_null = lm(price ~ stars + borough, data = nyc_airbnb)

fit_alternative = lm(price ~ stars + borough + room_type, data = nyc_airbnb)

anova(fit_null, fit_alternative) |> 
  broom::tidy()

```

# Borough-level differences
* to add an interaction term

```{r}
fit = 
  nyc_airbnb |> 
  lm(price ~ stars * borough + room_type * borough, data = _)

fit |> 
  broom::tidy()
```
this is kind of a lot; can get the same results but easier to read format by doing the following below

so...instead for exploratory analysis we'll fit a diff linear model for each borough and look at the effect of stars and room type on price
doesn't tell you stat signif just exploratory

fit a lm to each df; there is one df for each borough
results gives us just the output of the model we care about
```{r}
airbnb_lm = function(df) {
  lm(price ~ stars + room_type, data = df)
}

nyc_airbnb |> 
  nest(df = -borough) |> 
  mutate(
    models = map(df, airbnb_lm),
    results = map(models, broom::tidy)
  ) |> 
  select(borough, results) |> 
  unnest(results) |> 
  select(borough, term, estimate) |> 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) |> 
  knitr::kable(digits = 2)
  
  

```


same thing but just a little diff using an anonymous function
allows you to incorporate the function; don't have to actually write or save the functio separatley
does not save the function
```{r}
nyc_airbnb |> 
  nest(df = -borough) |> 
  mutate(
    models = map(df, \(df) lm(price ~ stars + room_type, data = df)),
    results = map(models, broom::tidy)
  ) |> 
  select(borough, results) |> 
  unnest(results) |> 
  select(borough, term, estimate) |> 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) |> 
  knitr::kable(digits = 2)
```

# Homicides in Baltimore
look at categorical outcome; binary

give you 1 if true and 0 if false
```{r}
baltimore_df = 
  read_csv("data/homicide-data.csv") |> 
  filter(city == "Baltimore") |> 
  mutate(
    resolved = as.numeric(disposition == "Closed by arrest"),
    victim_age = as.numeric(victim_age),
    victim_race = fct_relevel(victim_race, "White")) |> 
  select(resolved, victim_age, victim_race, victim_sex)
```

fitting a logistic regression
```{r}
fit_logistic = 
  baltimore_df |> 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = _, family = binomial()) 
  
  
```

```{r}
fit_logistic |> 
  broom::tidy() |> 
  mutate(OR = exp(estimate)) |> 
  select(term, estimate, OR)
```











